A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-16 survey.tex
Improving table format and ladder figures

A typical StarCraft map is defined as a rectangular grid, where the $width \times height$ of the map is measured in the number of $32 \times 32$ square of pixels, also knows as build tiles. Although the
resolution  at which  units  move  is in squares of $8 \times 8$ pixels, also knows as walk tiles. The typical dimensions for maps range from $64 \times 64$ to $256 \times 256$ build tiles. Each player  can
control up  to 200 units (plus an unlimited number of buildings).  Moreover, each
different race  contains between 30  to 35 different types  of units
and  buildings,  each  one  with  a significant  number  of  special
abilities. All these factors  together make StarCraft a significant
challenge,   in   which   humans    are   still   much   better   than
computers. For instance, in the game ladder iCCup\footnote{http://www.iccup.com/StarCraft/} where users are ranked by their current point totals ($E$ being the lowest possible rank, and $A^+$ and $Olympic$ being the second highest and highest ranks, respectively), the best StarCraft AI bots are ranked between $D$ and $D^+$, where average  amateur players are  ranked between $C^+$ and  $B$. For comparison, StarCraft professional  players are usually ranked between
$A^-$ and $A^+$.

@@

\begin{table}[t!]
\caption{Results of the AIIDE 2010 competition.}
\label{tab:aiide2010}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|}
\hline
Position & bot\\ \hline
1 & Overmind \\
2 & Krasi0 \\
3 & Chronos \\ \hline
\end{tabular}
\end{center}
\end{small}
\end{table}

@@

@@

@@

\begin{table}[t!]
\caption{Results of the AIIDE 2011 competition.}
\label{tab:aiide2011}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|}
\hline
Position & bot & win \% \\ \hline
1 & Skynet & 88.9\% \\
2 & UAlbertaBot & 79.4\% \\
3 & AIUR & 70.3\% \\
4 & ItayUndermind & 65.8\% \\
5 & EISBot & 60.6\% \\ \hline
\end{tabular}
\end{center}
\end{small}
\end{table}

@@

@@

\begin{table}[t!]
\caption{Results of the AIIDE 2012 competition.}
\label{tab:aiide2012}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|}
\hline
Position & bot & win \% \\ \hline
1 & Skynet & 84.4\% \\
2 & AIUR & 72.2\% \\
3 & UAlbertaBot & 68.6\% \\
4 & BroodwarBotQ & 59.1\% \\
5 & AdjutantBot & 52.8\% \\ \hline
\end{tabular}
\end{center}
\end{small}
\end{table}

\begin{table}[b]
\caption{Results of the CIG 2011 final round.}
\label{tab:cig-final-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|r|}
\hline
Position & crashes & games & bot	& win\%\\ \hline
1 & 0 &  30 &	 Skynet	  		&  86.7\%\\
2 & 0 &	 30 &	 UAlbertaBot 	&  73.3\%\\
3 & 3 &	 30 &	 Xelnaga  		&  36.7\%\\
4 & 2 &	 30 &	 BroodwarBotQ  	&  3.3\%\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table}

\begin{table*}[t]
\caption{Results of the first round at CIG 2011, held in two brackets.
Qualified for the final round: UAlbertaBot and Skynet (from A), Xelnaga
and BroodwarBotQ (from B, the latter by comparing direct encounters
with BTHAI of which 6:4 were won).}
\label{tab:cig-first-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|r|}
\hline
\multicolumn{5}{|c|}{Bracket A} \\ \hline
Position & crashes & games & bot	& win\%\\ \hline
A1 & 0 &	 40 &	 UAlbertaBot & 82.5\% \\
A2 & 1 &  	 40 &	 Skynet	  &  77.5\% \\
A3 & 2 &	 40 &	 AIUR	  &  60.0\% \\
A4 & 1 &	 40 &	 Nova	  &  20.0\% \\
A5 & 0 &	 40 &	 LSAI	  &  10.0\%\\
\hline
\end{tabular}
% bracket B
\begin{tabular}{|l|c|c|c|r|}
\hline
\multicolumn{5}{|c|}{Bracket B} \\ \hline
Position & crashes & games & bot	& win\%\\ \hline
B1 & 12 &	 40 &	 Xelnaga &	 62.5\%\\
B2 & 3 &   40 &	 BroodwarBotQ  &  57.5\%\\
B3 & 0 &	 40 &	 BTHAI	  &  57.5\%\\
B4 & 17 &	 40 &	 Protoss Beast Jelly  & 42.5\%\\
B5 & 0 &	 40 &	 EvoBot	  &  30.0\%\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table*}

@@

@@

\begin{table}[b]
\caption{Results of the CIG 2012 competition.}
\label{tab:cig2012}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|}
\hline
Position & bot & win \% \\ \hline
1 & Skynet & 78.3\% \\
2 & UAlbertaBot & 65.2\% \\
3 & AIUR & 60.4\% \\
4 & Adjutant & 58.6\% \\
5 & Nova & 52.4\% \\ \hline
\end{tabular}
\end{center}
\end{small}
\end{table}

\begin{figure*}[t]
	%\vspace*{-2ex}
    \centering
    \includegraphics[width=0.32\textwidth]{figures/vstable3.pdf}
    \includegraphics[width=0.32\textwidth]{figures/vstable6.pdf}
    \includegraphics[width=0.32\textwidth]{figures/vstable.pdf}
	%\vspace*{-4ex}
    \caption{Win percentages of CIG 2012 competition, from left
    to right: 3-player maps only, 6-player maps only, all maps.
    Read from line to column, bot in row wins given fraction of
    games against bot in column. For some bots, we find interesting
    differences, e.g. Xelnaga gets worse on 6-player maps, UAlbertaBot
    gets better. Only Xelnaga can reliably beat Skynet, but only on 
    3-player maps}
    \label{fig:cig2012-mapresults}
\end{figure*}

@@

@@

\begin{figure*}[tb]
    \centering
    \includegraphics[width=\textwidth]{figures/botLadder1.pdf}
    \caption{StarCraft Bot Ladder: bot's Elo Rating from February 1, 2012 to June 20, 2012}
    \label{fig:botLadder1}
\end{figure*}

\begin{figure*}[tb]
    \centering
    \includegraphics[width=\textwidth]{figures/botLadder2.pdf}
    \caption{StarCraft Bot Ladder: bot's Elo Rating from September 1, 2012 to January 10, 2013}
    \label{fig:botLadder2}
\end{figure*}

>>>>

A typical StarCraft map is defined as a rectangular grid, where the $width \times height$ of the map is measured in the number of $32 \times 32$ square of pixels, also knows as build tiles. Although the
resolution of walkable areas is in squares of $8 \times 8$ pixels, also knows as walk tiles. The typical dimensions for maps range from $64 \times 64$ to $256 \times 256$ build tiles. Each player  can
control up  to 200 units (plus an unlimited number of buildings).  Moreover, each
different race  contains between 30  to 35 different types  of units
and  buildings,  each  one  with  a significant  number  of  special
abilities. All these factors  together make StarCraft a significant
challenge,   in   which   humans    are   still   much   better   than
computers. For instance, in the game ladder iCCup\footnote{http://www.iccup.com/StarCraft/} where users are ranked by their current point totals ($E$ being the lowest possible rank, and $A^+$ and $Olympic$ being the second highest and highest ranks, respectively), the best StarCraft AI bots are ranked between $D$ and $D^+$, where average  amateur players are  ranked between $C^+$ and  $B$. For comparison, StarCraft professional  players are usually ranked between
$A^-$ and $A^+$.

@@

@@

\begin{table}[!t]
\caption{Results of the AIIDE 2010 competition}
\label{tab:aiide2010}
\centering
\begin{tabular}{|c|l|}
\hline
{\bfseries Position} & {\bfseries Bot}\\
\hline
1 & Overmind \\
2 & Krasi0 \\
3 & Chronos \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!b]
\caption{Results of the AIIDE 2011 competition}
\label{tab:aiide2011}
\centering
\begin{tabular}{|c|l|r|}
\hline
{\bfseries Position} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
1 & Skynet & 88.9\% \\
2 & UAlbertaBot & 79.4\% \\
3 & AIUR & 70.3\% \\
4 & ItayUndermind & 65.8\% \\
5 & EISBot & 60.6\% \\
\hline
\end{tabular}
\end{table}

@@

@@

\begin{table}[!t]
\caption{Results of the AIIDE 2012 competition}
\label{tab:aiide2012}
\centering
\begin{tabular}{|c|l|r|}
\hline
{\bfseries Position} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
1 & Skynet & 84.4\% \\
2 & AIUR & 72.2\% \\
3 & UAlbertaBot & 68.6\% \\
4 & BroodwarBotQ & 59.1\% \\
5 & AdjutantBot & 52.8\% \\
\hline
\end{tabular}
\end{table}

@@

@@

\begin{table*}[!t]
\caption{Results of the first round at CIG 2011, held in two brackets.
Qualified for the final round: UAlbertaBot and Skynet (from A), Xelnaga
and BroodwarBotQ (from B, the latter by comparing direct encounters
with BTHAI of which 6:4 were won)}
\label{tab:cig-first-round}
\centering
% bracket A
\begin{tabular}{|c|c|c|l|r|}
\hline
\multicolumn{5}{|c|}{Bracket A} \\ \hline
{\bfseries Position} & {\bfseries Crashes} & {\bfseries Games} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
A1 & 0 &   40 &  UAlbertaBot & 82.5\% \\
A2 & 1 &     40 &  Skynet   &  77.5\% \\
A3 & 2 &   40 &  AIUR   &  60.0\% \\
A4 & 1 &   40 &  Nova   &  20.0\% \\
A5 & 0 &   40 &  LSAI   &  10.0\%\\
\hline
\end{tabular}
% bracket B
\begin{tabular}{|c|c|c|l|r|}
\hline
\multicolumn{5}{|c|}{Bracket B} \\ \hline
{\bfseries Position} & {\bfseries Crashes} & {\bfseries Games} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
B1 & 12 &  40 &  Xelnaga &   62.5\%\\
B2 & 3 &   40 &  BroodwarBotQ  &  57.5\%\\
B3 & 0 &   40 &  BTHAI    &  57.5\%\\
B4 & 17 &  40 &  Protoss Beast Jelly  & 42.5\%\\
B5 & 0 &   40 &  EvoBot   &  30.0\%\\
\hline
\end{tabular}
\end{table*}

@@

\begin{figure*}[b]
	%\vspace*{-2ex}
    \centering
    \includegraphics[width=0.32\textwidth]{figures/vstable3.pdf}
    \includegraphics[width=0.32\textwidth]{figures/vstable6.pdf}
    \includegraphics[width=0.32\textwidth]{figures/vstable.pdf}
	%\vspace*{-4ex}
    \caption{Win percentages of CIG 2012 competition, from left
    to right: 3-player maps only, 6-player maps only, all maps.
    Read from line to column, bot in row wins given fraction of
    games against bot in column. For some bots, we find interesting
    differences, e.g. Xelnaga gets worse on 6-player maps, UAlbertaBot
    gets better. Only Xelnaga can reliably beat Skynet, but only on 
    3-player maps}
    \label{fig:cig2012-mapresults}
\end{figure*}

@@

\begin{table}[!b]
\caption{Results of the CIG 2011 competition}
\label{tab:cig-final-round}
\centering
\begin{tabular}{|c|c|c|l|r|}
\hline
{\bfseries Position} & {\bfseries Crashes} & {\bfseries Games} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
1 & 0 &  30 &  Skynet       &  86.7\%\\
2 & 0 &  30 &  UAlbertaBot  &  73.3\%\\
3 & 3 &  30 &  Xelnaga      &  36.7\%\\
4 & 2 &  30 &  BroodwarBotQ   &  3.3\%\\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[t]
\caption{Results of the CIG 2012 competition.}
\label{tab:cig2012}
\centering
\begin{tabular}{|c|l|r|}
\hline
{\bfseries Position} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
1 & Skynet & 78.3\% \\
2 & UAlbertaBot & 65.2\% \\
3 & AIUR & 60.4\% \\
4 & Adjutant & 58.6\% \\
5 & Nova & 52.4\% \\ 
\hline
\end{tabular}
\end{table}

\begin{figure*}[tb]
    \centering
    \includegraphics[width=\textwidth]{figures/botLadder1.pdf}
    \caption{Bot's Elo Rating from February 1, 2012 to June 20, 2012}
    \label{fig:botLadder1}
\end{figure*}

\begin{figure*}[tb]
    \centering
    \includegraphics[width=\textwidth]{figures/botLadder2.pdf}
    \caption{Bot's Elo Rating from September 1, 2012 to January 10, 2013}
    \label{fig:botLadder2}
\end{figure*}
